Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Replace Fig: collapse profile

\subsection{Post-Bounce Collapse Profile:
  Testing Scattering}
\label{ssec:test_collapse}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
Plot in Fig.~\ref{fig:avg_eps_collapse}.

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-collapse_profile-avg_eps_vs_cosA}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    in the collapse profile test.
    The observer is at 500~km, and the shock at 150~km,
    so that the half-opening angle of the shock is $\cos A=0.954$.
    The four methods depicted are 1) a fiducial Monte Carlo calculation,
    ray tracing using the 2) spectral and 3) gray methods to estimate background
    fields for scattering, and 4) ray tracing neglecting scattering.
    Test described in Sec.~\ref{ssec:test_collapse}}
  \label{fig:avg_eps_collapse}
\end{figure}

>>>>

\subsection{Post-Bounce Collapse Profile:
  Testing Scattering}
\label{ssec:test_collapse}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
\todo{clarify inelastic scattering and velocity terms}
Plot in Fig.~\ref{fig:avg_eps_collapse}.

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-collapse_profile_avg_eps_vs_cosA}
  \caption{Average energies in the collapse profile test,
    Sec.~\ref{ssec:test_collapse}.
    The observer is at 500~km, and the shock at 150~km,
    so that the half-opening angle of the shock is $\cos A=0.954$.
    The four methods depicted are 1) a fiducial Monte Carlo calculation,
    ray tracing using the 2) spectral and 3) gray methods to estimate background
    fields for scattering, and 4) ray tracing neglecting scattering.
  }
  \label{fig:avg_eps_collapse}
\end{figure}
